\scuba: iterative map-making with the Sub-Millimetre User Reduction Facility

### 2012-09-11 smurf_paper.tex
Thank an extra person

The James Clerk Maxwell Telescope is operated by the Joint Astronomy
Centre on behalf of the Science and Technology Facilities Council of
the United Kingdom, the Netherlands Organisation for Scientific
Research, and the National Research Council of Canada. Additional
funds for the contruction of \scuba\ were provided by the Canada
Foundation for Innovation. EC thanks CANARIE/CANFAR for additional
funding. This research was supported in part by the Natural Sciences
and Engineering Research Council of Canada. EC also thanks Matthew
Hasselfield and Mark Halpern for helpful discussions about multiplexed
TES arrays and their noise characteristics.  The authors thank the
members of the SCUBA-2 commissioning team for testing the map-maker
and reporting anomalies; in particular Antonio Chrysostomou and
Jessica Dempsey. We also thank Dennis Kelly, Alex van Engelen and
Jennifer Balfour for work on the SCUBA-2 observation simulator; and
Mark Thompson, Craig Walther and S\'{e}verin Gaudet for being on the
Critical Design Review panel. Finally, we thank Per Friberg and Gary
Davis for their helpful comments on the manuscript.

>>>>

The James Clerk Maxwell Telescope is operated by the Joint Astronomy
Centre on behalf of the Science and Technology Facilities Council of
the United Kingdom, the Netherlands Organisation for Scientific
Research, and the National Research Council of Canada. Additional
funds for the contruction of \scuba\ were provided by the Canada
Foundation for Innovation. EC thanks CANARIE/CANFAR for additional
funding. This research was supported in part by the Natural Sciences
and Engineering Research Council of Canada. EC also thanks Matthew
Hasselfield and Mark Halpern for helpful discussions about multiplexed
TES arrays and their noise characteristics.  The authors thank the
members of the SCUBA-2 commissioning team for testing the map-maker
and reporting anomalies; in particular Antonio Chrysostomou,
Jessica Dempsey and Wayne Holland. We also thank Dennis Kelly, Alex van Engelen and
Jennifer Balfour for work on the SCUBA-2 observation simulator; and
Mark Thompson, Craig Walther and S\'{e}verin Gaudet for being on the
Critical Design Review panel. Finally, we thank Per Friberg and Gary
Davis for their helpful comments on the manuscript.
